Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-02-23 SIR_manuscript.tex
a bit more on results

\david{Details such as the fact that you used ggplot are not important to state in the main text.  On the other hand, there isn't a clear narrative here.  The reader should feel that a story is being told.}\ali{partially addressed?, feedback is welcomed}

@@

The explicit formula for the basic reproduction number, $\Rnum$ \eqref{R0}, provides an opportunity to study the influence of changes in the underlying parameters on the critical index of epidemic dynamics. We are interested in understanding the effect of parameters that can be realistically controlled by changing in isolation, \percap testing intensity and test resulting, i.e., $\eta\_c$ and $\eta\_w$, $\rho$ and $\omega$, respectively. The following Proposition is the direct result of taking partial derivative of $\Rnum$ \eqref{R0} with respect to selected parameters. Note that we used Taylor approximation of $\Rnum$ at $\rho=0$ due to the complexity of the expression and thus inconclusive.\david{in that case it would be good to establish numerically that the relationships given in the proposition are valid more generally, at least for reasonable parameter ranges}\ali{help}
See the appendix for details.

\david{More importantly, you really need to state in words what this proposition is saying.  The reader has to check the param table and think it through themselves.}
\begin{proposition}
\label{prop1}
Using the expression of $\Rnum$ \eqref{R0},
\begin{enumerate}
\item \label{p1:eta}
$\partial{\Rnum}/\partial{\eta\_c} \geq 0$ and $\partial{\Rnum}/\partial{\eta\_w} \geq 0$. 
\item \label{p1:rho}
$\partial{\Rnum}/\partial{\rho} \leq 0$ when $\rho \approx 0$.
\item \label{p1:omega}
$\partial{\Rnum}/\partial{\omega}$ can be positive or negative when $\rho \approx 0$.
\end{enumerate}
\end{proposition}

>>>>

\david{Details such as the fact that you used ggplot are not important to state in the main text.  On the other hand, there isn't a clear narrative here.  The reader should feel that a story is being told.}\ali{addressed?, feedback is welcomed}

@@

The explicit formula for the basic reproduction number, $\Rnum$ \eqref{R0}, provides an opportunity to study the influence of changes in the underlying parameters on the critical index of epidemic dynamics. We are interested in understanding the effect of parameters that can be realistically controlled by changing in isolation, \percap testing intensity and test resulting, i.e., $\eta\_c$ and $\eta\_w$, $\rho$ and $\omega$, respectively. The following Proposition is the direct result of taking partial derivative of $\Rnum$ \eqref{R0} with respect to selected parameters. Note that we used Taylor approximation of $\Rnum$ at $\rho=0$ due to the complexity of the expression and thus inconclusive.\david{in that case it would be good to establish numerically that the relationships given in the proposition are valid more generally, at least for reasonable parameter ranges}\ali{will do the simulation for testing intensity $>>1$}
See the appendix for details.

\david{More importantly, you really need to state in words what this proposition is saying.  The reader has to check the param table and think it through themselves.}
\begin{proposition}
\label{prop1}
For model \eqref{model}, and by using the expression of the basic reproduction number $\Rnum$ \eqref{R0} ,
\begin{enumerate}
\item \label{p1:eta} increasing the relative probabilities of transmission for tested individuals, increases $\Rnum$;
$$\partial{\Rnum}/\partial{\eta\_c} \geq 0 \text{~and~} \partial{\Rnum}/\partial{\eta\_w} \geq 0.$$ 
\item \label{p1:rho} higher rate of testing reduces $\Rnum$;
$$\partial{\Rnum}/\partial{\rho} \leq 0 \text{~when~} \rho \approx 0.$$
\item \label{p1:omega} The rate of test return may result in the disease becomes extinct or not;
$$\partial{\Rnum}/\partial{\omega} \text{~can be positive or negative when~} \rho \approx 0.$$
\end{enumerate}
\end{proposition}
